\bf An Examination of Sport Climbing Competition Format and Scoring System

### 2021-07-31 manuscript/Rmd/draft.Rmd
Break
Late night

```{r setup, include=FALSE}
# install.packages(c("rticles", "xtable", "GGally", "patchwork", "cowplot"))
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE,
                      comment = "",
                      fig.height = 4,
                      fig.width = 5,
                      results = "asis")
options(xtable.comment = FALSE,
        xtable.caption.placement = "top", 
        xtable.include.rownames = FALSE)
```

@@

[//]: (I think this paragraph and the next should get moved somewhere else (or removed)  Maybe in the conclusions?  Definitely for the blog post include this, but I'm not sure how much of this needs to be in the actual article)
These three different climbing disciplines demand different sets of skills and, often, athletes specialize in a single event. However, since only one set of Olympic medals is awarded to sport climbing, rather than choosing only one of these disciplines to include in the Olympics, all three events were chosen to be included as a sort of climbing triathlon.

@@

The 8 climbers with the lowest score (i.e. lowest product of ranks across the three discplines) in the qualification round advance to the finals where they once again compete in all three disciplines. The final score for each person in the final stage is determined by multiplying their ranks in each discipline, similar to the qualification round, with the main difference being that there are only 8 competitors in the final as opposed to 20 in the qualification round.  The climbers with the lowest, second lowest, and third lowest product of ranks in the final wins the gold, silver, and bronze medal, respectively.

@@

Some individual sports such as the decathlon and heptathlon rely on a sum of scores from the ten or seven events, however, these scores are not determined based on the ranks of the competitiors.  That is a decathlete's score is entirely based upon their times, distances, and heights, and their overall score will be exactly the same if the times, distances, and heights remain the same regardless of the performance of other individuals.  Full details of dacathlon scoring can be found in @westera2006.

@@

```{r}
library(tidyverse)
library(xtable)
theme_set(theme_minimal())
```

@@

```{r}
mosaic::favstats(score ~ round, data = qual_final)[-10] %>% 
  xtable(caption = "Descriptive statistics of simulated scores for qualification and final rounds") %>% 
  print()
```

@@

```{r}
qual %>% 
  rename(Rank = rank) %>% 
  group_by(Rank) %>% 
  summarize(`Average score` = mean(score)) %>% 
  filter(Rank <= 10) %>% 
  xtable(caption = "The average scores for the top 10 qualification ranks according to our simulations. A climber will secure a finalist spot if they finish in the top 8.") %>% 
  print()
```

@@

```{r}
final %>% 
  rename(Rank = rank) %>% 
  group_by(Rank) %>% 
  summarize(`Average score` = mean(score)) %>% 
  xtable(caption = "The average scores for all final ranks according to our simulations. Ranks 1, 2, and 3 are table positions that guarantee medalist status for climbers.") %>% 
  print()
```

@@

For our analysis on the relationship between the rankings of the events and the final result, we used data from the 2018 Youth Olympics Women's Qualification. Figure 2 is a scatterplot and correlation matrix between the ranks of the individual events and the final standings, with Kendall’s Tau [@kendall1938] as our measure of ordinal association between the quantities. It is evidently clear that there exists a strong and positive correlation between the ranks of bouldering and lead climbing, and as a results, the standings of these two events are highly correlated with the final rankings. On the other hand, the correlation with the final rank is not as strong for speed climbing as the other two events. Thus, speed climbers are facing a huge disadvantage in this scoring system, compared to those that are specialized in the other two concentrations. This validates the concerns of climbers in the interview mentioned in Section \ref{introduction}

This trend also holds for most of the past competitions. (add table to the appendix)

@@

@@

>>>>

```{r setup, include=FALSE}
# install.packages(c("rticles", "kableExtra", "GGally", "patchwork", "cowplot"))
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE,
                      comment = "",
                      fig.height = 4,
                      fig.width = 5,
                      fig.align = "center")
options(scipen = 999)
```

@@

<!-- 
(I think this paragraph and the next should get moved somewhere else (or removed)  Maybe in the conclusions?  Definitely for the blog post include this, but I'm not sure how much of this needs to be in the actual article) 
These three different climbing disciplines demand different sets of skills and, often, athletes specialize in a single event. However, since only one set of Olympic medals is awarded to sport climbing, rather than choosing only one of these disciplines to include in the Olympics, all three events were chosen to be included as a sort of climbing triathlon. 
-->

@@

The 8 climbers with the lowest score (i.e. lowest product of ranks across the three disciplines) in the qualification round advance to the finals where they once again compete in all three disciplines. The final score for each person in the final stage is determined by multiplying their ranks in each discipline, similar to the qualification round, with the main difference being that there are only 8 competitors in the final as opposed to 20 in the qualification round.  The climbers with the lowest, second lowest, and third lowest product of ranks in the final wins the gold, silver, and bronze medal, respectively.

@@

Some individual sports such as the decathlon and heptathlon rely on a sum of scores from the ten or seven events, however, these scores are not determined based on the ranks of the competitors.  That is a decathlete's score is entirely based upon their times, distances, and heights, and their overall score will be exactly the same if the times, distances, and heights remain the same regardless of the performance of other individuals.  Full details of decathlon scoring can be found in @westera2006.

@@

```{r}
library(tidyverse)
library(kableExtra)
theme_set(theme_minimal())
```

@@

```{r}
mosaic::favstats(score ~ round, data = qual_final)[-10] %>% 
  kable(caption = "Descriptive statistics of simulated scores for qualification and final rounds",
        booktabs = TRUE)
```

@@

```{r}
qual %>% 
  rename(Rank = rank) %>% 
  group_by(Rank) %>% 
  summarize(`Average score` = mean(score)) %>% 
  filter(Rank <= 10) %>% 
  kable(caption = "The average scores for the top 10 qualification ranks according to our simulations. A climber will secure a finalist spot if they finish in the top 8.",
        booktabs = TRUE)
```

@@

```{r}
final %>% 
  rename(Rank = rank) %>% 
  group_by(Rank) %>% 
  summarize(`Average score` = mean(score)) %>% 
  kable(caption = "The average scores for all final ranks according to our simulations. Ranks 1, 2, and 3 are table positions that guarantee medalist status for climbers.",
        booktabs = TRUE)
```

@@

For our analysis on the relationship between the rankings of the events and the final result, we used data from the 2018 Youth Olympics Women's Qualification. Figure 2 is a scatterplot and correlation matrix between the ranks of the individual events and the final standings, with Kendall’s Tau [@kendall1938] as our measure of ordinal association between the quantities. It is evidently clear that there exists a strong and positive correlation between the ranks of bouldering and lead climbing, and as a results, the standings of these two events are highly correlated with the final rankings. On the other hand, the correlation with the final rank is not as strong for speed climbing as the other two events. Thus, speed climbers are facing a huge disadvantage in this scoring system, compared to those that are specialized in the other two concentrations. This validates the concerns of climbers in the interview mentioned in Section \ref{introduction}. We also have evidence for these correlations from the qualification rounds of the 2018 Asian Games (Table 4), 2019 World Championship (Table 5), 2020 European Championship (Table 6), and 2020 Pan-American Championships (Table 7).

@@

Recommendations: climbers were right, need a change in format

@@

```{r}
print_cor <- function(event = "", 
                      gender = c("men_qual", "women_qual"),
                      title = "") {
  path <- "https://raw.githubusercontent.com/qntkhvn/climbing/main/data/"
  men <- read_csv(paste0(path, event, "/", gender[1], ".csv")) %>% 
    select(Overall = rank, Speed = speed, Bouldering = bould, Lead = lead) %>% 
    drop_na() %>% 
    cor(method = "kendall") %>% 
    as_tibble() %>% 
    round(4)
  women <- read_csv(paste0(path, event, "/", gender[2], ".csv")) %>% 
    select(Overall = rank, Speed = speed, Bouldering = bould, Lead = lead) %>% 
    drop_na() %>% 
    cor(method = "kendall") %>% 
    as_tibble() %>% 
    round(4)
  out <- cbind(men, women)
  rownames(out) <- c("Overall", "Speed", "Bouldering", "Lead")
  kable(out, caption = title, booktabs = TRUE, position = "H") %>% 
    add_header_above(c("", "Men" = 4, "Women" = 4)) %>%
    kable_styling(latex_options = c("repeat_header", "scale_down"))
}
```

```{r}
print_cor("2018_asiad", title = "This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2018 Asian Games")
```

```{r}
print_cor("2019_world", title = "This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2019 World Championships")
```

```{r}
print_cor("2020_europe", title = "This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 European Championship")
```

```{r}
print_cor("2020_pan_american", title = "This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 Pan American Championship")
```

### 2021-07-31 manuscript/Rmd/draft.tex
Late night

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

@@

These three different climbing disciplines demand different sets of
skills and, often, athletes specialize in a single event. However, since
only one set of Olympic medals is awarded to sport climbing, rather than
choosing only one of these disciplines to include in the Olympics, all
three events were chosen to be included as a sort of climbing triathlon.

@@

The 8 climbers with the lowest score (i.e.~lowest product of ranks
across the three discplines) in the qualification round advance to the
finals where they once again compete in all three disciplines. The final
score for each person in the final stage is determined by multiplying
their ranks in each discipline, similar to the qualification round, with
the main difference being that there are only 8 competitors in the final
as opposed to 20 in the qualification round. The climbers with the
lowest, second lowest, and third lowest product of ranks in the final
wins the gold, silver, and bronze medal, respectively.

@@

Some individual sports such as the decathlon and heptathlon rely on a
sum of scores from the ten or seven events, however, these scores are
not determined based on the ranks of the competitiors. That is a
decathlete's score is entirely based upon their times, distances, and
heights, and their overall score will be exactly the same if the times,
distances, and heights remain the same regardless of the performance of
other individuals. Full details of dacathlon scoring can be found in
\citet{westera2006}.

@@

\begin{table}[ht]
\centering
\caption{Descriptive statistics of simulated scores for qualification and final rounds} 
\begin{tabular}{lrrrrrrrr}
  \hline
round & min & Q1 & median & Q3 & max & mean & sd & n \\ 
  \hline
Qualification & 1.00 & 240.00 & 684.00 & 1638.00 & 8000.00 & 1158.84 & 1273.48 & 200000 \\ 
  Final & 1.00 & 24.00 & 60.00 & 126.00 & 512.00 & 91.12 & 91.35 & 80000 \\ 
   \hline
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Histogram of simulated scores for qualification and final
rounds}
\end{figure}

@@

\begin{table}[ht]
\centering
\caption{The average scores for the top 10 qualification ranks according to our simulations. A climber will secure a finalist spot if they finish in the top 8.} 
\begin{tabular}{rr}
  \hline
Rank & Average score \\ 
  \hline
  1 & 36.02 \\ 
    2 & 73.61 \\ 
    3 & 115.40 \\ 
    4 & 162.23 \\ 
    5 & 216.00 \\ 
    6 & 278.16 \\ 
    7 & 350.33 \\ 
    8 & 434.59 \\ 
    9 & 532.14 \\ 
   10 & 642.33 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{The average scores for all final ranks according to our simulations. Ranks 1, 2, and 3 are table positions that guarantee medalist status for climbers.} 
\begin{tabular}{rr}
  \hline
Rank & Average score \\ 
  \hline
  1 & 9.67 \\ 
    2 & 20.41 \\ 
    3 & 33.26 \\ 
    4 & 50.59 \\ 
    5 & 74.76 \\ 
    6 & 110.05 \\ 
    7 & 164.43 \\ 
    8 & 265.78 \\ 
   \hline
\end{tabular}
\end{table}

@@

For our analysis on the relationship between the rankings of the events
and the final result, we used data from the 2018 Youth Olympics Women's
Qualification. Figure 2 is a scatterplot and correlation matrix between
the ranks of the individual events and the final standings, with
Kendall's Tau \citep{kendall1938} as our measure of ordinal association
between the quantities. It is evidently clear that there exists a strong
and positive correlation between the ranks of bouldering and lead
climbing, and as a results, the standings of these two events are highly
correlated with the final rankings. On the other hand, the correlation
with the final rank is not as strong for speed climbing as the other two
events. Thus, speed climbers are facing a huge disadvantage in this
scoring system, compared to those that are specialized in the other two
concentrations. This validates the concerns of climbers in the interview
mentioned in Section \ref{introduction}

This trend also holds for most of the past competitions. (add table to
the appendix)

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{Kendall's rank correlations - 2018 World Championship, Men's
and Women's Qualifications}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{This figure illustrates the changes to the final rankings of
the 2018 Youth Olympics Men's and Women's Finals when we leave out one
climber. For each gender competition, each panel represents the rank of
the drop-out athlete, with 0 being the original final results. Each case
with a change in rank orderings is highlighted by a black panel border,
and any player with a rank change is represented by a red-filled bar}
\end{figure}

@@

@@

>>>>

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\usepackage{caption}
\captionsetup[figure]{skip=3pt}
\usepackage{float}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

@@

The 8 climbers with the lowest score (i.e.~lowest product of ranks
across the three disciplines) in the qualification round advance to the
finals where they once again compete in all three disciplines. The final
score for each person in the final stage is determined by multiplying
their ranks in each discipline, similar to the qualification round, with
the main difference being that there are only 8 competitors in the final
as opposed to 20 in the qualification round. The climbers with the
lowest, second lowest, and third lowest product of ranks in the final
wins the gold, silver, and bronze medal, respectively.

@@

Some individual sports such as the decathlon and heptathlon rely on a
sum of scores from the ten or seven events, however, these scores are
not determined based on the ranks of the competitors. That is a
decathlete's score is entirely based upon their times, distances, and
heights, and their overall score will be exactly the same if the times,
distances, and heights remain the same regardless of the performance of
other individuals. Full details of decathlon scoring can be found in
\citet{westera2006}.

@@

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-4}Descriptive statistics of simulated scores for qualification and final rounds}
\centering
\begin{tabular}[t]{lrrrrrrrr}
\toprule
round & min & Q1 & median & Q3 & max & mean & sd & n\\
\midrule
Qualification & 1 & 240 & 684 & 1638 & 8000 & 1158.84378 & 1273.47884 & 200000\\
Final & 1 & 24 & 60 & 126 & 512 & 91.12077 & 91.35293 & 80000\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[H]

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-5-1}

}

\caption{Histogram of simulated scores for qualification and final rounds}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-6}The average scores for the top 10 qualification ranks according to our simulations. A climber will secure a finalist spot if they finish in the top 8.}
\centering
\begin{tabular}[t]{rr}
\toprule
Rank & Average score\\
\midrule
1 & 36.0187\\
2 & 73.6111\\
3 & 115.3954\\
4 & 162.2263\\
5 & 216.0041\\
\addlinespace
6 & 278.1649\\
7 & 350.3272\\
8 & 434.5932\\
9 & 532.1383\\
10 & 642.3298\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-7}The average scores for all final ranks according to our simulations. Ranks 1, 2, and 3 are table positions that guarantee medalist status for climbers.}
\centering
\begin{tabular}[t]{rr}
\toprule
Rank & Average score\\
\midrule
1 & 9.6748\\
2 & 20.4143\\
3 & 33.2648\\
4 & 50.5933\\
5 & 74.7620\\
\addlinespace
6 & 110.0536\\
7 & 164.4274\\
8 & 265.7760\\
\bottomrule
\end{tabular}
\end{table}

@@

For our analysis on the relationship between the rankings of the events
and the final result, we used data from the 2018 Youth Olympics Women's
Qualification. Figure 2 is a scatterplot and correlation matrix between
the ranks of the individual events and the final standings, with
Kendall's Tau \citep{kendall1938} as our measure of ordinal association
between the quantities. It is evidently clear that there exists a strong
and positive correlation between the ranks of bouldering and lead
climbing, and as a results, the standings of these two events are highly
correlated with the final rankings. On the other hand, the correlation
with the final rank is not as strong for speed climbing as the other two
events. Thus, speed climbers are facing a huge disadvantage in this
scoring system, compared to those that are specialized in the other two
concentrations. This validates the concerns of climbers in the interview
mentioned in Section \ref{introduction}. We also have evidence for these
correlations from the qualification rounds of the 2018 Asian Games
(Table 4), 2019 World Championship (Table 5), 2020 European Championship
(Table 6), and 2020 Pan-American Championships (Table 7).

\begin{figure}[H]

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-9-1}

}

\caption{Kendall's rank correlations - 2018 World Championship, Men's and Women's Qualifications}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-12-1}

}

\caption{This figure illustrates the changes to the final rankings of the 2018 Youth Olympics Men's and Women's Finals when we leave out one climber. For each gender competition, each panel represents the rank of the drop-out athlete, with 0 being the original final results. Each case with a change in rank orderings is highlighted by a black panel border, and any player with a rank change is represented by a red-filled bar}\label{fig:unnamed-chunk-12}
\end{figure}

@@

\newpage

@@

\newpage

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-14}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2018 Asian Games}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.5731 & 0.6760 & 0.6126 & 1.0000 & 0.5474 & 0.6878 & 0.7053\\
Speed & 0.5731 & 1.0000 & 0.3022 & 0.2174 & 0.5474 & 1.0000 & 0.2540 & 0.2947\\
Bouldering & 0.6760 & 0.3022 & 1.0000 & 0.6203 & 0.6878 & 0.2540 & 1.0000 & 0.6878\\
Lead & 0.6126 & 0.2174 & 0.6203 & 1.0000 & 0.7053 & 0.2947 & 0.6878 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-15}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2019 World Championships}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.2632 & 0.3684 & 0.3474 & 1.0000 & 0.2316 & 0.5013 & 0.2526\\
Speed & 0.2632 & 1.0000 & -0.0947 & -0.3263 & 0.2316 & 1.0000 & 0.0686 & -0.4526\\
Bouldering & 0.3684 & -0.0947 & 1.0000 & 0.2000 & 0.5013 & 0.0686 & 1.0000 & 0.2902\\
Lead & 0.3474 & -0.3263 & 0.2000 & 1.0000 & 0.2526 & -0.4526 & 0.2902 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-16}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 European Championship}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.0947 & 0.3810 & 0.2632 & 1.0000 & 0.1847 & 0.5358 & 0.5368\\
Speed & 0.0947 & 1.0000 & -0.1587 & -0.4316 & 0.1847 & 1.0000 & -0.1915 & -0.0897\\
Bouldering & 0.3810 & -0.1587 & 1.0000 & 0.2751 & 0.5358 & -0.1915 & 1.0000 & 0.5040\\
Lead & 0.2632 & -0.4316 & 0.2751 & 1.0000 & 0.5368 & -0.0897 & 0.5040 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[H]

\caption{\label{tab:unnamed-chunk-17}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 Pan American Championship}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.5906 & 0.5556 & 0.6491 & 1.0000 & 0.5789 & 0.6140 & 0.5906\\
Speed & 0.5906 & 1.0000 & 0.2164 & 0.4035 & 0.5789 & 1.0000 & 0.2632 & 0.3099\\
Bouldering & 0.5556 & 0.2164 & 1.0000 & 0.2749 & 0.6140 & 0.2632 & 1.0000 & 0.3918\\
Lead & 0.6491 & 0.4035 & 0.2749 & 1.0000 & 0.5906 & 0.3099 & 0.3918 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}
